---
title: "Figures of manuscript *scalable diagnosis of acute myeloid leukemia using high-dimensional machine learning and blood transcriptomics*"
author: "Stefanie Warnat-Herresthal"
output: 
  html_document: 
    toc: true
    toc_float: true
    theme: united

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ggplot2)
```

Loading data

```{r}
result <- read.delim("../results/results_summary.txt", sep = "\t")
```


# Main figures
## Figure 2 B: Dataset 1, all samples
Random Sampling vs. Cross-study sampling
```{r}
dat <- result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 1 & 
                result$samples == "all" &
                result$setting %in% c("random_sampling","cross-study-sampling"),]

# mean for between 1000 and 2000
dat$size.ts.mean <- dat$size.ts
dat$size.ts.mean[which(dat$setting == "cross-study-sampling" & dat$size.ts > 1000 & dat$size.ts <= 2000)] <- mean(dat$size.ts[which(dat$setting == "cross-study-sampling" & dat$size.ts > 1000 & dat$size.ts <= 2000)])

# maximum value: 

mean(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 1 & 
                result$samples == "all" &
                result$setting == "random_sampling" &
         result$classifier == "LASSO" &
         result$size.ts == 2000,]$value)

ggplot(dat[dat$measure %in% c("ACC") & 
              dat$classifier == "LASSO" & 
              dat$setting %in% c("random_sampling", "cross-study-sampling") &
              dat$dataset == 1 &
              dat$samples == "all",], 
       aes(x = size.ts.mean, y = value, color = setting)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.5, 1), xlim = c(0, 2000)) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Figure 2 B: Random sampling vs. cross-study sampling, Dataset 1, all samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Fig2B.pdf", height = 4, width = 6)

```

## Figure 2 C: Dataset 1, leukemia samples
Random Sampling vs. Cross-study sampling
```{r}

mean(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 1 & 
                result$samples == "leukemia" &
                result$setting == "random_sampling" &
         result$classifier == "LASSO" &
         result$size.ts == 1741,]$value)


dat <- result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 1 & 
                result$samples == "leukemia" &
                result$setting %in% c("random_sampling","cross-study-sampling"),]


# mean for between 1000 and 2000
dat$size.ts.mean <- dat$size.ts
dat$size.ts.mean[which(dat$setting == "cross-study-sampling" & dat$size.ts > 1000 & dat$size.ts <= 2000)] <- mean(dat$size.ts[which(dat$setting == "cross-study-sampling" & dat$size.ts > 1000 & dat$size.ts <= 2000)])

ggplot(dat[dat$measure %in% c("ACC") & 
              dat$classifier == "LASSO" & 
              dat$setting %in% c("random_sampling", "cross-study-sampling") &
              dat$dataset == 1 &
              dat$samples == "leukemia",], 
       aes(x = size.ts.mean, y = value, color = setting)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.5, 1), xlim = c(0, 2000)) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Figure 2 C Dataset 1, leukemia samples")

#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Fig2C.pdf", height = 4, width = 6)

```
## Figure 2 D: Dataset 2, all samples
Random Sampling vs. Cross-study sampling
```{r}

mean(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 2 & 
                result$samples == "all" &
                result$setting == "random_sampling" &
         result$classifier == "LASSO" &
         result$size.ts == 6679,]$value)



dat <- result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 2 & 
                result$samples == "all" &
                result$setting %in% c("random_sampling","cross-study-sampling"),]

# mean for between 1000 and 2000
dat$size.ts.mean <- dat$size.ts
dat$size.ts.mean[which(dat$setting == "cross-study-sampling" & dat$size.ts > 4000 & dat$size.ts <= 6000)] <- mean(dat$size.ts[which(dat$setting == "cross-study-sampling" & dat$size.ts > 4000 & dat$size.ts <= 6000)])


ggplot(dat[dat$measure %in% c("ACC") & 
              dat$classifier == "LASSO" & 
              dat$setting %in% c("random_sampling", "cross-study-sampling") &
              dat$dataset == 2 &
              dat$samples == "all",], 
       aes(x = size.ts.mean, y = value, color = setting)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.5, 1)) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Figure 2 D, DS2, all samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Fig2D.pdf", height = 4, width = 6)

```

## Figure 2 E: Dataset 2, leukemia samples
Random Sampling vs. Cross-study sampling
```{r}

mean(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 2 & 
                result$samples == "leukemia" &
                result$setting == "random_sampling" &
         result$classifier == "LASSO" &
         result$size.ts == 2000,]$value)





dat <- result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 2 & 
                result$samples == "leukemia" &
                result$setting %in% c("random_sampling","cross-study-sampling"),]

# mean for between 1000 and 2000
dat$size.ts.mean <- dat$size.ts
dat$size.ts.mean[which(dat$setting == "cross-study-sampling" & dat$size.ts > 1000 & dat$size.ts <= 2000)] <- mean(dat$size.ts[which(dat$setting == "cross-study-sampling" & dat$size.ts > 1000 & dat$size.ts <= 2000)])

ggplot(dat[dat$measure %in% c("ACC") & 
              dat$classifier == "LASSO" & 
              dat$setting %in% c("random_sampling", "cross-study-sampling") &
              dat$dataset == 2 &
              dat$samples == "leukemia",], 
       aes(x = size.ts.mean, y = value, color = setting)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.5, 1)) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Figure 2 E, DS2, leukemia samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Fig2E.pdf", height = 4, width = 6)

```
## Figure 2 F: Dataset 3, all samples
Random Sampling vs. Cross-study sampling
```{r}
mean(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 3 & 
                result$samples == "all" &
                result$setting == "random_sampling" &
         result$classifier == "LASSO" &
         result$size.ts == 945,]$value)




dat <- result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 3 & 
                result$samples == "all" &
                result$setting %in% c("random_sampling","cross-study-sampling"),]

# mean for between 1000 and 2000
dat$size.ts.mean <- dat$size.ts
dat$size.ts.mean[which(dat$setting == "cross-study-sampling" & dat$size.ts > 500 & dat$size.ts <= 1000)] <- mean(dat$size.ts[which(dat$setting == "cross-study-sampling" & dat$size.ts > 500 & dat$size.ts <= 1000)])

ggplot(dat[dat$measure %in% c("ACC") & 
              dat$classifier == "LASSO" & 
              dat$setting %in% c("random_sampling", "cross-study-sampling") &
              dat$dataset == 3 &
              dat$samples == "all",], 
       aes(x = size.ts.mean, y = value, color = setting)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.5, 1)) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Figure 2 F, DS3, all samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Fig2F.pdf", height = 4, width = 6)

```

## Figure 3: PPV



## Figure 4
```{r}
ggplot(result[result$measure %in% c("ACC") & 
              result$classifier == "LASSO" & 
              result$setting %in% c("cross-platform-sampling"),],
       aes(x = size.ts, y = value, color = setting)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.5, 1)) + 
  facet_grid(dataset~samples) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Figure 2 F, DS3, all samples")
# ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Fig2F.pdf", height = 4, width = 6)

```

# Supplementary Figures 
## Random sampling, Dataset 1, all samples

```{r}
library(ggplot2)
ggplot(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 1 & 
                result$samples == "all" &
                result$setting == "random_sampling",], 
       aes(x = size.ts, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  
  
#  geom_smooth(aes(group = measure)) + 
  coord_cartesian(ylim = c(0.5, 1)) + 
  facet_wrap(~classifier, nrow = 3) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Dataset 1 random sampling, all samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Randomsampling_all_DS1.pdf", height = 4, width = 6)

```

## Random sampling, Dataset 1, leukemia samples

```{r}
ggplot(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 1 & 
                result$samples == "leukemia" &
                result$setting == "random_sampling",], 
       aes(x = size.ts, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.5, 1)) + 
  facet_wrap(~classifier, nrow = 3) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Dataset 1 random sampling, all samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Randomsampling_leukemia_DS1.pdf", height = 4, width = 6)
```

## Random sampling, Dataset 2, all samples

```{r}
library(ggplot2)
ggplot(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 2 & 
                result$samples == "all" &
                result$setting == "random_sampling",], 
       aes(x = size.ts, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  
  
#  geom_smooth(aes(group = measure)) + 
  coord_cartesian(ylim = c(0.5, 1)) + 
  facet_wrap(~classifier, nrow = 3) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Dataset 2 random sampling, all samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Randomsampling_all_DS2.pdf", height = 4, width = 6)
```


## Random sampling, Dataset 2, leukemia samples

```{r}
ggplot(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 2 & 
                result$samples == "leukemia" &
                result$setting == "random_sampling",], 
       aes(x = size.ts, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  
  
#  geom_smooth(aes(group = measure)) + 
  coord_cartesian(ylim = c(0.5, 1)) + 
  facet_wrap(~classifier, nrow = 3) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Dataset 2 random sampling, leukemia samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Randomsampling_leukemia_DS2.pdf", height = 4, width = 6)
```


## Random sampling, Dataset 3, all samples (WAIT FOR LDA!)

```{r}

ggplot(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 3 & 
                result$samples == "all" &
                result$setting == "random_sampling",], 
       aes(x = size.ts, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") +
  #geom_point() + 
  
  
#  geom_smooth(aes(group = measure)) + 
# coord_cartesian(ylim = c(0.2, 1)) + 
  facet_wrap(~classifier, nrow = 3) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Dataset 3 random sampling, all samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Randomsampling_all_DS3.pdf", height = 4, width = 6)
```



## Cross-study sampling, Dataset 1, all samples

```{r}

# give mean training set size: 
dat <- result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 1 & 
                result$samples == "all" &
                result$setting == "cross-study-sampling",]

# mean for between 1000 and 2000
dat$size.ts.mean <- dat$size.ts
dat$size.ts.mean[which(dat$size.ts > 1000 & dat$size.ts <= 2000)] <- mean(dat$size.ts[which(dat$size.ts > 1000 & dat$size.ts <= 2000)])

ggplot(dat[dat$measure %in% c("ACC", "SENS", "SPEC") & 
                dat$dataset == 1 & 
                dat$samples == "all" &
                dat$setting == "cross-study-sampling",], 
       aes(x = size.ts.mean, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  facet_wrap(~classifier, nrow = 3) + 
  coord_cartesian(ylim = c(0.5, 1)) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Dataset 1 cross-study sampling, all samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Cross-Study-sampling_all_DS1.pdf", height = 4, width = 6)

```


## Cross-study sampling, Dataset 1, leukemia samples

```{r}

# give mean training set size: 
dat <- result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 1 & 
                result$samples == "leukemia" &
                result$setting == "cross-study-sampling",]

# mean for between 1000 and 1500
dat$size.ts.mean <- dat$size.ts
dat$size.ts.mean[which(dat$size.ts > 1000 & dat$size.ts <= 2000)] <- mean(dat$size.ts[which(dat$size.ts > 1000 & dat$size.ts <= 2000)])

ggplot(dat[dat$measure %in% c("ACC", "SENS", "SPEC") & 
                dat$dataset == 1 & 
                dat$samples == "leukemia" &
                dat$setting == "cross-study-sampling",], 
       aes(x = size.ts.mean, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.5, 1)) + 
  facet_wrap(~classifier, nrow = 3) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Dataset 1 cross-study sampling, leukemia samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Cross-Study-sampling_leukemia_DS1.pdf", height = 4, width = 6)

```


## Cross-study sampling, Dataset 2, all samples

```{r}
dat <- result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 2 & 
                result$samples == "all" &
                result$setting %in% c("cross-study-sampling"),]

# mean for between 1000 and 2000
dat$size.ts.mean <- dat$size.ts
dat$size.ts.mean[which(dat$setting == "cross-study-sampling" & dat$size.ts > 4000 & dat$size.ts <= 6000)] <- mean(dat$size.ts[which(dat$setting == "cross-study-sampling" & dat$size.ts > 4000 & dat$size.ts <= 6000)])


ggplot(dat[dat$measure %in% c("ACC", "SENS", "SPEC") & 
                dat$dataset == 2 & 
                dat$samples == "all" &
                dat$setting == "cross-study-sampling",], 
       aes(x = size.ts.mean, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.5, 1)) + 
  facet_wrap(~classifier, nrow = 3) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Dataset 2 cross-study sampling, all samples")

#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Cross-Study-sampling_all_DS2.pdf", height = 4, width = 6)

```


## Cross-study sampling, Dataset 2, leukemia samples

```{r}

dat <- result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 2 & 
                result$samples == "leukemia" &
                result$setting == "cross-study-sampling",]


# mean for between 1000 and 2000
dat$size.ts.mean <- dat$size.ts
dat$size.ts.mean[which(dat$size.ts > 1000 & dat$size.ts <= 2000)] <- mean(dat$size.ts[which(dat$size.ts > 1000 & dat$size.ts <= 2000)])


ggplot(dat[dat$measure %in% c("ACC", "SENS", "SPEC") & 
                dat$dataset == 2 & 
                dat$samples == "leukemia" &
                dat$setting == "cross-study-sampling",], 
       aes(x = size.ts.mean, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.5, 1)) + 
  facet_wrap(~classifier, nrow = 3) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Dataset 2 cross-study sampling, leukemia samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Cross-Study-sampling_leukemia_DS2.pdf", height = 4, width = 6)

```
## Cross-study sampling, Dataset 3, leukemia samples

```{r}
dat <- result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == 3 & 
                result$samples == "all" &
                result$setting == "cross-study-sampling",]

# mean for between 1000 and 1500
dat$size.ts.mean <- dat$size.ts
dat$size.ts.mean[which(dat$size.ts > 500 & dat$size.ts <= 1000)] <- mean(dat$size.ts[which(dat$size.ts > 500 & dat$size.ts <= 1000)])


ggplot(dat[dat$measure %in% c("ACC", "SENS", "SPEC") & 
                dat$dataset == 3 & 
                dat$samples == "all" &
                dat$setting == "cross-study-sampling",], 
       aes(x = size.ts.mean, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.0, 1)) + 
  facet_wrap(~classifier, nrow = 3) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Dataset 3 cross-study sampling, all samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Cross-Study-sampling_all_DS3.pdf", height = 4, width = 6)

```

## Cross-platform sampling, TS Dataset 1, VS Dataset 2, raw samples

```{r}

ggplot(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == "1_2" & 
                result$samples == "raw" &
                result$setting == "cross-platform-sampling",], 
       aes(x = size.ts, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  facet_wrap(~classifier, nrow = 3) + 
  coord_cartesian(ylim = c(0.2, 1)) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Cross-platform sampling, TS 1, VS 2 , raw samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Cross-Platform_raw_DS1_2.pdf", height = 4, width = 6)

```


## Cross-platform sampling, TS Dataset 1, VS Dataset 2, ranked samples

```{r}

ggplot(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == "1_2" & 
                result$samples == "rank" &
                result$setting == "cross-platform-sampling",], 
       aes(x = size.ts, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.2, 1)) + 
  facet_wrap(~classifier, nrow = 3) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Cross-platform sampling, TS 1, VS 2 , ranked samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Cross-Platform_rank_DS1_2.pdf", height = 4, width = 6)

```


## Cross-platform sampling, TS Dataset 2, VS Dataset 3, raw samples

```{r}

ggplot(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == "2_3" & 
                result$samples == "raw" &
                result$setting == "cross-platform-sampling",], 
       aes(x = size.ts, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.2, 1)) + 
  facet_wrap(~classifier, nrow = 3) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Cross-platform sampling, TS 2, VS 3 , raw samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Cross-Platform_raw_DS2_3.pdf", height = 4, width = 6)

```

## Cross-platform sampling, TS Dataset 2, VS Dataset 3, ranked samples

```{r}

ggplot(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == "2_3" & 
                result$samples == "rank" &
                result$setting == "cross-platform-sampling",], 
       aes(x = size.ts, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  facet_wrap(~classifier, nrow = 3) + 
  coord_cartesian(ylim = c(0.2, 1)) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Cross-platform sampling, TS 2, VS 3 , ranked samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Cross-Platform_rank_DS2_3.pdf", height = 4, width = 6)

```


## Cross-platform sampling, TS Dataset 1, VS Dataset 3, raw samples

```{r}

ggplot(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == "1_3" & 
                result$samples == "raw" &
                result$setting == "cross-platform-sampling",], 
       aes(x = size.ts, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.2, 1)) + 
  facet_wrap(~classifier, nrow = 3) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Cross-platform sampling, TS 1, VS 3 , raw samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Cross-Platform_raw_DS1_3.pdf", height = 4, width = 6)

```



## Cross-platform sampling, TS Dataset 1, VS Dataset 3, raw samples

```{r}

ggplot(result[result$measure %in% c("ACC", "SENS", "SPEC") & 
                result$dataset == "1_3" & 
                result$samples == "rank" &
                result$setting == "cross-platform-sampling",], 
       aes(x = size.ts, y = value, color = measure)) + 
  stat_summary(fun.y = mean, geom = "line") + 
  stat_summary(fun.data = mean_se, geom = "errorbar") + 
  coord_cartesian(ylim = c(0.2, 1)) + 
  facet_wrap(~classifier, nrow = 3) + 
  theme(strip.background = element_rect(fill = "white"), 
        panel.background = element_rect(fill = "white", colour = "black")) + 
  ggtitle("Cross-platform sampling, TS 1, VS 3 , ranked samples")
#ggsave("E:/Stefanie/Classifier/Paper/Plots_all_calculations/Cross-Platform_rank_DS1_3.pdf", height = 4, width = 6)

```
